Untitled

### 2024-01-22 README.Rmd
remove broken link
resolves issue #905

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://cranchecks.info/badges/worst/taxize)](https://cranchecks.info/pkgs/taxize)
[![R-CMD-check](https://github.com/ropensci/taxize/workflows/R-CMD-check/badge.svg)](https://github.com/ropensci/taxize/actions/)
[![codecov](https://codecov.io/gh/ropensci/taxize/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/taxize)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@

The taxize book: https://taxize.dev

>>>>

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![cran checks](https://badges.cranchecks.info/worst/taxize.svg)](https://cran.r-project.org/web/checks/check_results_taxize.html)
[![rworkflows](https://github.com/ropensci/taxize/workflows/rworkflows/badge.svg)](https://github.com/ropensci/taxize/actions/)
[![codecov](https://codecov.io/gh/ropensci/taxize/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ropensci/taxize)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/taxize)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/taxize)](https://cran.r-project.org/package=taxize)

@@
